Differentiable Optics with {\Large $\partial$}Lux: I - Deep Calibration of Flat Field and Phase Retrieval with Automatic Differentiation

### 2023-04-14 src/tex/ms.tex
[showyourwork] overleaf sync

In this series of papers, we present a new software package, \dlux, for fitting high-dimensional parametrized physical optics models to astronomical data. By using the Python library \textsc{Jax}\cite{jax}, we obtain \ac{gpu} hardware acceleration, as well as automatic differentiation or `autodiff' \cite{Margossian2018} features that enable high-dimensional optimization and inference with gradient descent or \ac{hmc}. In the present paper, we focus on the particular problem of estimating the \ac{prf} and \ac{psf} simultaneously - i.e. joint flat field calibration and phase retrieval. In Paper~II, we will show how autodiff enables improvements to hardware \textit{design}, directly calculating and optimizing the Fisher information and therefore fundamental figures of merit of an optical system end-to-end. And in subsequent papers, we will use this for end-to-end deconvolution of high angular resolution imaging with an unknown \ac{psf}. We make \dlux available as open-source software on GitHub\footnote{\href{https://github.com/LouisDesdoigts/dLux}{github.com/LouisDesdoigts/dLux}}, and encourage interested readers to use and contribute to this package as a community resource. This paper has been compiled using ShowYourWork \cite{Luger2021}, so that all figures link to the code used to produce themcan be found \href{https://github.com/LouisDesdoigts/instrumental_calibration/tree/main}{here}.

>>>>

In this series of papers, we present a new software package, \dlux, for fitting high-dimensional parametrized physical optics models to astronomical data. By using the Python library \textsc{Jax}\cite{jax}, we obtain \ac{gpu} hardware acceleration, as well as automatic differentiation or `autodiff' \cite{Margossian2018} features that enable high-dimensional optimization and inference with gradient descent or \ac{hmc}. In the present paper, we focus on the particular problem of estimating the \ac{prf} and \ac{psf} simultaneously - i.e. joint flat field calibration and phase retrieval. In Paper~II, we will show how autodiff enables improvements to hardware \textit{design}, directly calculating and optimizing the Fisher information and therefore fundamental figures of merit of an optical system end-to-end. And in subsequent papers, we will use this for end-to-end deconvolution of high angular resolution imaging with an unknown \ac{psf}. We make \dlux available as open-source software on GitHub\footnote{\href{https://github.com/LouisDesdoigts/dLux}{github.com/LouisDesdoigts/dLux}}, and encourage interested readers to use and contribute to this package as a community resource. This paper has been compiled using ShowYourWork \cite{Luger2021}, so that all figures link to the code used to produce them can be found \href{https://github.com/LouisDesdoigts/instrumental_calibration/tree/main}{here}.
